D_exp_2

### 2018-08-20 experiments/D_exp_2/writeup/D_exp_2.Rmd
foo

The variables are:
Vagueness 2 levels (X) sumcoded -.5, +.5 
Item 4 levels (Y) 
Selection 2 levels (Z)

@@

```{r}
dat$XYZ <- with(dat, factor(paste(Vagueness,Item,Selection)))
```

Convert a K level factor Y into a sum-coding representation.

```{r}
Item.numeric <- sapply(dat$Item,function(i) contr.sum(4)[i,])
dat$Item1 <- Item.numeric[1,]
dat$Item2 <- Item.numeric[2,]
dat$Item3 <- Item.numeric[3,]
```

```{r}
dat_model <- dat
Item.numeric <- sapply(dat_model$Item,function(i) contr.sum(4)[i,])
dat_model$Item1 <- Item.numeric[1,]
dat_model$Item2 <- Item.numeric[2,]
dat_model$Item3 <- Item.numeric[3,]
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))

null.model <- lmer(RT_log ~ 
                     Item1 + c_Vag:Item1 +
                     Item2 + c_Vag:Item2 + 
                     Item3 + c_Vag:Item3 + 
                     c_Sel + c_Vag:c_Sel + 
                     (1 + c_Vag * c_Itm * c_Sel|Subject), dat_model, REML=FALSE)
pretty_coef_table(null.model, "null model")

full.model <- lmer(RT_log ~ 
                     Item1 + c_Vag:Item1 +
                     Item2 + c_Vag:Item2 + 
                     Item3 + c_Vag:Item3 + 
                     c_Sel + c_Vag:c_Sel + c_Vag +
                     (1 + c_Vag * c_Itm * c_Sel|Subject), dat_model, REML=FALSE)
pretty_coef_table(full.model, "full model")

anova(null.model, full.model)
```

>>>>

The variables are:
Vagueness 2 levels (X) 
Item 4 levels (Y) 
Selection 2 levels (Z)

@@

```{r}
#dat$XYZ <- with(dat, factor(paste(Vagueness,Item,Selection)))
```

```{r}
dat_model <- subset(dat, select=c(Subject, Item, Vagueness, Selection, RT_log))

Item.numeric <- sapply(dat_model$Item,function(i) contr.sum(4)[i,])
dat_model$Item1 <- Item.numeric[1,]
dat_model$Item2 <- Item.numeric[2,]
dat_model$Item3 <- Item.numeric[3,]

Selection.numeric <- sapply(dat_model$Selection,function(i) contr.sum(2)[i,])
dat_model$Selection1 <- Selection.numeric[]

Vagueness.numeric <- sapply(dat_model$Vagueness,function(i) contr.sum(2)[i,])
dat_model$Vagueness1 <- Vagueness.numeric[]

dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))

head(dat_model)
```

```{r, "null model 0"}
# make the null model
null.model <- lmer(RT_log ~ 
                     Item1 + Vagueness1:Item1 +
                     Item2 + Vagueness1:Item2 + 
                     Item3 + Vagueness1:Item3 + 
                     Selection1 + Vagueness1:Selection1 + 
                     (Vagueness1 * Selection1 * c_Itm |Subject), dat_model, REML=FALSE)
pretty_coef_table(null.model, "null model")
```

```{r, "full model0"}
# make the full model
full.model <- lmer(RT_log ~ 
                     Item1 + Vagueness1:Item1 +
                     Item2 + Vagueness1:Item2 + 
                     Item3 + Vagueness1:Item3 + 
                     Selection1 + Vagueness1:Selection1 + Vagueness1 +
                     (Vagueness1 * Selection1 * c_Itm |Subject), dat_model, REML=FALSE)
pretty_coef_table(full.model, "full model")
```

```{r}
# do model comparison between the null and full models
anova(null.model, full.model)
```
